A thesis draft

### 2018-12-03 res/sections/15-ArchitecturalImplementation.tex
Add prof corrections (#15)
- Fix #14 - Add prof corrections
- Fix #13 - Swap table columns, add saved configurations
Add two missing corrections

\section{Architecture introduction}

Before devling into the details of the actual implementation, we briefly
introduce some of its functional components and the way they work.

@@

\paragraph*{Low-layer orchestrator}
The low-layer orchestrator job corresponds to the one defined in the ETSI MANO
definition, with the role of managing and orchestrating VNFs and NSs. The
low-layer MANO holds different data repositories where VNF and NS definitions
are stored, alongside with various monitoring tools, logs and network services
repositories. The low layer MANO exposes a set of APIs to the upper layer
(related to handling services) MANO, that is able to configure and manage the
services. In other words, the service MANO has the possibility to configure and
launch services to the low-layer orchestrator, providing the necessary
information.

>>>>

\section{A top-down overview}

Before digging into the details of the actual implementation, we briefly
introduce some of its functional components and the way they work.

@@

\paragraph*{Low-layer orchestrator}
The low-layer orchestrator job corresponds to the one defined in the ETSI MANO,
with the role of managing and orchestrating VNFs and NSs. The low-layer MANO
holds different data repositories where VNF and NS definitions are stored,
alongside with various monitoring tools, logs and network services repositories.
The low layer MANO exposes a set of APIs to the upper layer (related to handling
services) MANO, that is able to configure and manage the services. In other
words, the service MANO has the possibility to configure and launch services to
the low-layer orchestrator, providing the necessary information.
